Quantifying social distancing behaviour across Australia in response to COVID-19

### 2020-04-28 manuscript/ms.Rmd

@@

 - Announcement timeline for Australia

>>>>

#### NBN

The National Broadband Network Co. (NBN) is the Australian national wholesale open-access data network, providing broadband access to retail service providers. The majority of its traffic is through wired broadband connections. As such, these connections are static in place, and they offer internet access to a broad mixture of users. NBN provided a time series (with a temporal resolution of 15 minutes) to aggregated data relating to mean upload and download traffic volume generated by houshold customers, aggregated spatiall by ABS Statistical Area 2 (SA2) region, and excluding data points generated by less than 600 customers.

Full-day NBN data for the period from September 1, 2019, until March 24th, 2020 have been used.

@@

Governmental controls in response to COVID-19 in Australia started in January 2020. On January 20th, 2020, the Australian government imposed restrictions on flights from the Wuhan region of China. The first case was identified in Australia shortly after, on January 25th. Queensland declared a *State of emergency* on January 29th, and travel restrictions from China were imposed on February 1st. Enforced measures were imposed from March 16th, with a ban on non-essential gatherings, with Victoria declaring a *State of emergency* on the same day, and closing schools from March 22nd. From the 22th of March, Stage 1 restricitons were mandated (closures of pubs, restaurants, except takeaway, and adivsing on social distancing). This was escalated to Stage 2 from March 26th, with mandatory social distancing and closures of museums, galleries, and additional services. On March 31st, Stage 3 restrictions were imposed, with enforcdeable stay at home measures.
